A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
Remove seemingly unnecessary number column from regressor table
We need to shrink that table further

\begin{tabular}{llllllllllll}

@@

\textbf{no} & \textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

@@

1 & adja & \aTagAdja & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII \tabularnewline
2 & adjd & \aTagAdjd & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII \tabularnewline
3 & adv & \aTagAdv & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII \tabularnewline
4 & appr & \aTagAppr & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII \tabularnewline
5 & apprart & preposition with article & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII \tabularnewline
6 & art & \aTagArt & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII \tabularnewline
7 & kon & \aTagKon & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII \tabularnewline
8 & ne & \aTagNe & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII \tabularnewline
9 & nn & \aTagNn & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII \tabularnewline
10 & pds & substituting demonstrative pronoun & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII \tabularnewline
11 & pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII \tabularnewline
12 & pper & \aTagPper & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII \tabularnewline
13 & pposat & \aTagPposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII \tabularnewline
14 & prf & reflexive personal pronoun & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII \tabularnewline
15 & ptkvz & \aTagPtkvz & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII \tabularnewline
16 & vafin & \aTagVafin & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII \tabularnewline
17 & vmfin & finite verb, modal & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII \tabularnewline
18 & vvfin & \aTagVvfin & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII \tabularnewline
19 & vvinf & \aTagVvinf & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII \tabularnewline
20 & vvpp & \aTagVvpp & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII \tabularnewline
21 & tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
\cline{1-12}
22 & sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
23 & phones & 80 most often occuring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
24 & no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
\cline{1-12}
25 & fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
26 & fg\_ad\_rms & root mean square & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII \tabularnewline

>>>>

\small

@@

\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

@@

adja & \aTagAdja & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII \tabularnewline
adjd & \aTagAdjd & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII \tabularnewline
adv & \aTagAdv & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII \tabularnewline
appr & \aTagAppr & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII \tabularnewline
apprart & preposition with article & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII \tabularnewline
art & \aTagArt & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII \tabularnewline
kon & \aTagKon & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII \tabularnewline
ne & \aTagNe & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII \tabularnewline
nn & \aTagNn & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII \tabularnewline
pds & substituting demonstrative pronoun & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII \tabularnewline
pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII \tabularnewline
pper & \aTagPper & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII \tabularnewline
pposat & \aTagPposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII \tabularnewline
prf & reflexive personal pronoun & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII \tabularnewline
ptkvz & \aTagPtkvz & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII \tabularnewline
vafin & \aTagVafin & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII \tabularnewline
vmfin & finite verb, modal & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII \tabularnewline
vvfin & \aTagVvfin & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII \tabularnewline
vvinf & \aTagVvinf & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII \tabularnewline
vvpp & \aTagVvpp & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII \tabularnewline
tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
e{1-12}
sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
phones & 80 most often occuring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
e{1-12}
fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
fg\_ad\_rms & root mean square & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII \tabularnewline
